---
title: "Breakout session 2"
subtitle: "R Markdown"
output:
  xaringan::moon_reader:
    css: [default, rd.css, rd-font.css, "hygge"]
    lib_dir: assets
    seal: false
    nature:
      highlightStyle: dracula
      countIncrementalSlides: false
      beforeInit: "macros.js"
---


```{r include = FALSE, purl = FALSE}
source("_setup.R")
```

<!-- rmarkdown::render("_07_rmarkdown_exercise.Rmd") -->

---

class: inverse, center, middle

# Exercise

![:custom_hr]()




---

# Exercise

## Context

- *The goal of the exercise is to create a GitHub repo, add and render a `.Rmd` document in `.html` and create a github page*

--

- *To do this, we will use data on Palmer penguins from [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php) and the [Palmer Station, Antarctica LTER](https://pal.lternet.edu/).*

--

- *Data are available through the [`palmerpenguin`](https://github.com/allisonhorst/palmerpenguins) R package.*

```{r palmer, eval = FALSE}
library(palmerpenguins)
data(package = 'palmerpenguins')
```

---

# Exercise

## Context

```{r load, echo = FALSE}
library(palmerpenguins)
```
```{r head}
head(penguins)
```

---

# Exercise

## Task

.font90[
**1)** Create a new GitHub repository

**2)** In the new repository create a new R Markdown document named `index.Rmd`

**3)** Write a .font80[**YAML**] header including the document title, the authors, the date, and output format html

**4)** Include a single section (level 1) with the title of your choice using `# Title`
]


---

# Exercise

## Task

.font90[
**5)** Install the `palmerpenguins` R Package with `install.packages("palmerpenguins")`

**6)** Include a code chunk to add a graph of a the bill length of penguins as a function of their body mass :

````md
```{r graph, echo = FALSE, fig.height=3.5, fig.width=4, fig.align='center'}`r ''`
plot(x = penguins$body_mass_g,
     y = penguins$bill_length_mm,
     main = "Bill length as a function of body mass",
     xlab = "Body mass (g)",
     ylab = "Bill length (mm)",
     col = "#5d2756",
     bg = "#5d275699",
     pch = 21)
```
````
]

---

# Exercise

## Task

.font90[
**7)** Render a `.html` document named `index.html`

**8)** Commit and push changes made to the GitHub repository

**9)** Create GitHub page from `index.html`
]


```{r, echo = FALSE, purl = FALSE}
countdown::countdown(minutes = 30, seconds = 0)
```

---

# Exercise

## Solution

Load solution file here: [`r rfa("database")`](path/to/solution)
